\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Figure 2 fixed the aspect ratio

axes_obj <- gen_axes(  
  proj = projection * 5,
  limits = 0.15,
  axis_pos_x = -0.1,
  axis_pos_y = -0.075,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0.01)

@@

two_curvy_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#3182bd") +
  geom_point(
    #size = 0.2,
    alpha = 0.3,
    color = "#000000") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  interior_annotation("a") +
  theme(
    legend.position = "none"
  )

@@

axes_obj <- gen_axes(  
  proj = projection * 5,
  limits = 0.15,
  axis_pos_x = -0.1,
  axis_pos_y = -0.075,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0.01)

@@

two_curvy_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#3182bd") +
  geom_point(
    #size = 0.2,
    alpha = 0.3,
    color = "#000000") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  interior_annotation("b") +
  theme(
    legend.position = "none"
  )
```

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two views of the true model (blue lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the S-curve data (black points). The data is spread along the S shape, and does not vary much from this curve. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>)." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

>>>>

axes_obj <- gen_axes(  
  proj = projection * 5,
  limits = 0.15,
  axis_pos_x = -0.1,
  axis_pos_y = -0.1,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0.01)

@@

two_curvy_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#3182bd") +
  geom_point(
    #size = 0.2,
    alpha = 0.3,
    color = "#000000") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("a", cex = 2) +
  theme(
    legend.position = "none"
  )

@@

axes_obj <- gen_axes(  
  proj = projection * 5,
  limits = 0.12,
  axis_pos_x = -0.1,
  axis_pos_y = -0.1,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0.01)

@@

two_curvy_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#3182bd") +
  geom_point(
    #size = 0.2,
    alpha = 0.3,
    color = "#000000") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.125, 0.075)) + 
  ylim(c(-0.125, 0.075)) +
  interior_annotation("b", c(0.08, 0.93), cex = 2) +
  theme(
    legend.position = "none"
  )
```

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two views of the true model (blue lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the two-curvy data (black points). The data is spread along the S shape, and does not vary much from this curve. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>)." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

### 2024-09-26 paper.tex
Figure 2 fixed the aspect ratio

\caption{\label{fig-two-curvy-true-proj}Two views of the true model
(blue lines) in \(2\text{-}D\) projections from \(7\text{-}D\), for the
S-curve data (black points). The data is spread along the S shape, and
does not vary much from this curve. (The \textbf{langevitour} software
is used to view the data with a tour, and the full video is available at
\url{https://youtu.be/I5GL23vLiw0}).}

>>>>

\caption{\label{fig-two-curvy-true-proj}Two views of the true model
(blue lines) in \(2\text{-}D\) projections from \(7\text{-}D\), for the
two-curvy data (black points). The data is spread along the S shape, and
does not vary much from this curve. (The \textbf{langevitour} software
is used to view the data with a tour, and the full video is available at
\url{https://youtu.be/I5GL23vLiw0}).}
